Seasonality in governing upper-ocean dynamics at submesoscales

### 2016-06-09 writeup/rocha_etal.tex
Change the text accordingly
Updates bib

\begin{figure*}[ht]
\begin{center}
\hspace{-1.25cm}\includegraphics[width=.7\textwidth]{figs/fig1_1.pdf}\\
\vspace{-.125cm}
\includegraphics[width=.75\textwidth]{figs/fig1_2.pdf}
 \caption{(a) The study region with the subregion where the LLC outputs are
          analyzed. LLC 4320 (1/48$^\circ$) snapshots of surface vorticity (b and c) and a transect
          of potential density at 165$^\circ$E (d and e). The snapshots were
          taken at 00:00 UTC.}
\vspace{-1.5cm}
 \label{fig1}
 \end{center}
 \end{figure*}

@@

 \begin{figure*}[ht]
   \begin{center}
     \includegraphics[width=.75\textwidth]{figs/fig2.pdf}
  \caption{Time series of the root-mean-square (RMS) of vorticity (a) and
  lateral rate of strain (b), and horizontal divergence (c) in the LLC outputs and gridded AVISO data.}
  \label{fig2}
  \end{center}
\end{figure*}

@@

\section{Summary and Conclusion}
Our main finding is that
near-surface upper-ocean inertia-gravity waves, undergo
a strong seasonal cycle that is out-of-phase with the seasonal cycle of
the submesoscale turbulence. \cite{dasaro1978} showed that linear internal waves
velocity in the mixed-layer strongly depends on the density jump at the mixed-layer
base. In Summer, the shallow mixed-layer overlays a strong seasonal pycnocline,
and thus the internal waves projection onto the mixed-layer may be stronger
according to \cite{dasaro1978}'s argumets. An
alternative explanation is that the shape baroclinic modes experience significant
seasonal modulation, with significant summertime peak in their surface amplitude.
If the internal wave source has weak seasonal dependence, then a strong
seasonal cycle in the near-surface expression of internal waves is expected.
Internal tide generation is unlikely to vary significant seasonally, and therefore
it is plausible to expect a strong seasonality in the the near-surface expression of
 internal tides and
other small-scale internal waves generated through internal tide interactions.
Near-inertial wave generation peaks in Winter, but those waves project on large
horizontal scales. \textcolor{red}{(REFS)}.

@@

\begin{figure*}[ht]
  \begin{center}
    \includegraphics[width=.75\textwidth]{figs/fig3.pdf}
 \caption{Seasonal variation of joint probability distributions: vorticity vs.
          divergence (a through e) and vorticity vs. strain rate (f through j).
          Dashed lines in (a) through (e) represent $\delta = \frac{\omega}{f_0}
          \zeta$ where $\omega = 2\pi/$(12 h, 3 h) and $f_0$ is the inertial frequency
          in the middle of the domain (32.5$^\circ$ N). Dashed lines in (f) through (j)
          represent pure strain flow $\alpha = \zeta$.}
 \label{fig3}
 \end{center}
\end{figure*}

\begin{figure*}[ht]
  \begin{center}
    \includegraphics[width=.9\textwidth]{figs/fig4.pdf}
 \caption{Surface (horizontal) KE (a) and SSH variance wavenumber spectra (b)
 in the 1/48$^\circ$ simulation. Solid lines
 are spectra based on hourly snapshots, dashed lines are spectra based on daily-averaged
 fields.}
 \label{fig4}
 \end{center}
\end{figure*}

@@

@@

%%% End of body of article:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Optional Appendix goes here
%
% \appendix resets counters and redefines section heads
% but doesn't print anything.
% After typing \appendix
%
%\section{Here Is Appendix Title}
% will show
% Appendix A: Here Is Appendix Title
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Optional Glossary or Notation section, goes here
%
%%%%%%%%%%%%%%
% Glossary is only allowed in Reviews of Geophysics
% \section*{Glossary}
% \paragraph{Term}
% Term Definition here
%
%%%%%%%%%%%%%%
% Notation -- End each entry with a period.
% \begin{notation}
% Term & definition.\\
% Second term & second definition.\\
% \end{notation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  ACKNOWLEDGMENTS

>>>>

\begin{figure*}[ht]
\begin{center}
\hspace{-1.25cm}\includegraphics[width=.6\textwidth]{figs/fig1_1.pdf}\\
\vspace{-.125cm}
\includegraphics[width=.65\textwidth]{figs/fig1_2.pdf}
 \caption{(a) The study region with the subregion where the LLC outputs are
          analyzed. LLC 4320 (1/48$^\circ$) snapshots of surface vorticity (b and c) and a transect
          of potential density at 165$^\circ$E (d and e). The snapshots were
          taken at 00:00 UTC.}
\vspace{-1.5cm}
 \label{fig1}
 \end{center}
 \end{figure*}

@@

 \begin{figure*}[ht]
   \begin{center}
     \includegraphics[width=.65\textwidth]{figs/fig2.pdf}
  \caption{Time series of the root-mean-square (RMS) of vorticity (a) and
  lateral rate of strain (b), and horizontal divergence (c) in the LLC outputs and gridded AVISO data.}
  \label{fig2}
  \end{center}
\end{figure*}

@@

\section{Summary and Conclusion}
Our main finding is that
near-surface upper-ocean inertia-gravity waves, undergo
a strong seasonal cycle that is out-of-phase with the seasonal cycle of
the submesoscale turbulence. \cite{dasaro1978} showed that linear internal waves
velocity in the mixed-layer strongly depends on the density jump at the mixed-layer
base. In Summer, the shallow mixed-layer overlays a strong seasonal pycnocline,
and thus the internal waves projection onto the mixed-layer may be stronger
according to \cite{dasaro1978}'s arguments. An
alternative explanation is that the shape baroclinic modes experience significant
seasonal modulation, with significant summertime peak in their surface amplitude.
If the internal wave source has weak seasonal dependence, then a strong
seasonal cycle in the near-surface expression of internal waves is expected.
Internal tide generation is unlikely to vary significantlly seasonally \citep[e.g.,][]{alford2003},
and therefore it is plausible to expect a strong seasonality in the the near-surface
expression of internal tides and
other small-scale internal waves generated through internal tide interactions.
Near-inertial wave generation peaks in Winter, but those waves project on large
horizontal scales \citep[e.g, ][]{qi_etal1995}.

@@

\begin{figure*}[ht]
  \begin{center}
    \includegraphics[width=.6\textwidth]{figs/fig3.pdf}
 \caption{Seasonal variation of joint probability distributions: vorticity vs.
          divergence (a through e), vorticity vs. strain rate (f through l).
          and vorticity vs. laplacian of sea-surface height (m through r).
          Dashed lines in (a) through (e) represent $\delta = \frac{\omega}{f_0}
          \zeta$ where $\omega = 2\pi/$(12 h, 3 h) and $f_0$ is the inertial frequency
          in the middle of the domain (32.5$^\circ$ N). Dashed lines in (f) through (j)
          represent pure strain flow $\alpha = \zeta$.}
 \label{fig3}
 \end{center}
\end{figure*}

\begin{figure*}[ht]
  \begin{center}
    \includegraphics[width=.75\textwidth]{figs/fig4.pdf}
 \caption{Surface (horizontal) KE (a) and SSH variance wavenumber spectra (b)
 in the 1/48$^\circ$ simulation. Solid lines
 are spectra based on hourly snapshots, dashed lines are spectra based on daily-averaged
 fields.}
 \label{fig4}
 \end{center}
\end{figure*}

@@

%
%  ACKNOWLEDGMENTS

@@

%%% End of body of article:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Optional Appendix goes here
%
% \appendix resets counters and redefines section heads
% but doesn't print anything.
% After typing \appendix
%
%\section{Here Is Appendix Title}
% will show
% Appendix A: Here Is Appendix Title
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Optional Glossary or Notation section, goes here
%
%%%%%%%%%%%%%%
% Glossary is only allowed in Reviews of Geophysics
% \section*{Glossary}
% \paragraph{Term}
% Term Definition here
%
%%%%%%%%%%%%%%
% Notation -- End each entry with a period.
% \begin{notation}
% Term & definition.\\
% Second term & second definition.\\
% \end{notation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
